---
title: "Hierarchical Boosting"
author: "Marc Pybus"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

A Hierarchical Boosting framework for combining multiple tests for detecting positive selection.



```
     # load input dataset
     input_path <- system.file("exdata/training_data.txt", package="hierarchicalBoosting")
     input <- read.table(input_path,header=TRUE,stringsAsFactors=FALSE)
     
     # define individual boosting parameters
     boosting_1<-c()
     boosting_1["input_data"]<-"original"
     boosting_1["scenario_A"]<-"recent_complete,ancient_complete"
     boosting_1["scenario_B"]<-"neutral,recent_incomplete,ancient_incomplete"
     boosting_1["threshold_scenario_A"]<-FALSE
     boosting_1["threshold_scenario_B"]<-0.01
     
     boosting_2<-c()
     boosting_2["input_data"]<-"boosting_1:scenario_B"
     boosting_2["scenario_A"]<-"neutral"
     boosting_2["scenario_B"]<-"recent_incomplete,ancient_incomplete"
     boosting_2["threshold_scenario_A"]<-0.99
     boosting_2["threshold_scenario_B"]<-FALSE
     
     boosting_3<-c()
     boosting_3["input_data"]<-"boosting_1:scenario_A"
     boosting_3["scenario_A"]<-"recent_complete"
     boosting_3["scenario_B"]<-"ancient_complete"
     boosting_3["threshold_scenario_A"]<-0.95
     boosting_3["threshold_scenario_B"]<-0.05
     
     boosting_4<-c()
     boosting_4["input_data"]<-"boosting_2:scenario_B"
     boosting_4["scenario_A"]<-"recent_incomplete"
     boosting_4["scenario_B"]<-"ancient_incomplete"
     boosting_4["threshold_scenario_A"]<-0.95
     boosting_4["threshold_scenario_B"]<-0.05
     
     # create configuration table
     config_table<-data.frame(rbind(boosting_1,boosting_2,boosting_3,boosting_4),stringsAsFactors=FALSE)
     
     # define bootstrapping parameters
     bootstrap_iterations<-10
     bootstrap_sampling<-0.9
     
     # create hierarchicalBoosting object
     hierarchicalBoosting <- train.HierarchicalBoosting(input, config_table, bootstrap_iterations, bootstrap_sampling)
     
     #load empirical dataset
     input_empirical <- system.file("exdata/SLC45A2_CEU_sweep.txt", package="hierarchicalBoosting")
     empirical <- read.table(input_empirical,header=TRUE,stringsAsFactors=FALSE)
     
     # apply hierarchicalBoosting object to empirical dataset
     hierarchicalBoosting_results <- apply.HierarchicalBoosting(empirical, config_table, hierarchicalBoosting)
     
     # summarize hierarchicalBoosting results
     classification <- summarize.HierarchicalBoosting(hierarchicalBoosting_results)

```







----
Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
